QPLIB: A Library of Quadratic Programming Instances

### 2018-08-08 QPLIB-3.tex
Update QPLIB-3.tex

\textcolor{green}{We chose instances based on the following four goals:}
%During the development of the library, a discussion ensued about
%the expected goals that we wished to achieve. The following four goals
%were finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       \textcolor{green}{Thanks to these extensive preliminary tests, we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.}
       %We then filtered according to a first
       %measure of computational difficulty, i.e., we discarded all instances
       %that are solved by at least 30\% of the complete solvers within a time
       %limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       We carefully analyzed the instances one by one, and we clustered them
       according to their features; for each cluster we kept only a few
       representatives, e.g. by eliminating all but a few of those with very similar size and coming from the same donor.
       \textcolor{green}{The instances discarded by this second filter are instances of the same specific problem, e.g., we gathered many Max Cut Problem instances and we kept in the library only a representative small set of them. The selected representative instances are the larger and computationally harder ones.}
       Finally, in order to only
       keep computationally challenging instances we ran a complete solver for \textit{QGQ} with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $319$ discrete instances and
$134$ continuous instances.

>>>>

\textcolor{green}{We chose instances based on the following four goals:}
%During the development of the library, a discussion ensued about
%the expected goals that we wished to achieve. The following four goals
%were finally identified:
%
\begin{enumerate}
 \item to represent as far as possible all the different categories of QP
       problems;
 %
 \item to gather ``challenging'' instances, i.e., ones which can not be easily
       solved by  state-of-the-art solvers;
 %
 \item to include, for each of the categories, a set of well-diversified
       instances; and
 %
 \item to obtain a set of instances which is neither too small, so as to
       preserve statistical relevance, nor too large so as to being
       computationally manageable.
\end{enumerate}
%
To achieve such goals, we performed the following two filters, applied in
a cascade.
%
\begin{itemize}
 \item \emph{First Instances Filter.}\\
       The first filter was designed to drastically reduce the number of
       instances by eliminating the ``easy'' ones. An empirical measure
       for the hardness of an instance is the CPU time needed by a
       complete solver (cf.~\S\ref{sec:algo}) to solve it to
       global optimality. Accordingly, for each of the gathered instance we
       ran the complete solvers in GAMS, which number depends on the category
       of the instance under consideration, cf.~Table \ref{t:solvers}.
       \textcolor{green}{Thanks to these extensive preliminary tests, we discarded all instances
       that are solved by at least 30\% of the complete solvers within a time
       limit of 30 seconds.}
       %We then filtered according to a first
       %measure of computational difficulty, i.e., we discarded all instances
       %that are solved by at least 30\% of the complete solvers within a time
       %limit of 30 seconds.
 %
 \item \emph{Second Instances Filter.}\\
       The goal of the second filter was to eliminate ``similar'' instances.
       \textcolor{green}{We carefully analyzed the instances one by one,
       %, and we clustered them
       %according to their features; for each cluster we kept only a few
       %representatives, e.g. 
        eliminating all but a few of those with very similar size and coming from the same donor.
       The instances discarded by this second filter are instances of the same specific problem, e.g., we gathered many Max Cut Problem instances and we kept in the library only a representative small set of them. The selected representative instances are the larger and computationally harder ones.}
       Finally, in order to only
       keep computationally challenging instances we ran a complete solver for \textit{QGQ} with a time limit of 120 seconds; all the
       instances which have been solved to proven optimality within this time limit
       were discarded.
\end{itemize}
%
In Table~\ref{tab:filters} we summarize the two filter steps, which
allowed us to identify the final set of $319$ discrete instances and
$134$ continuous instances.
